---
title: "Sample Questions"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

#### Question 1 (10 marks)

Check the R code and results and answer the questions below.

```{r}
library(ggplot2)
str(diamonds)
```

(a) How many kinds  `cut' of diamonds in this data set, and how many observations collected in total? How many variables(attributes) are listed in the dataset? (3 marks)

Answer: 5 kinds (1 mark), 53940 observations in the data set (1 mark), 10 variables (1 mark).

(b) What is the name of the package we load below, and what is the name of the plot? Hint: Scatter plot or density plot or histogram? (3 marks)

```{r}
library(ggplot2) #load the package
ggplot(diamonds[1:100,], aes(x=carat, y=price, shape=cut)) + geom_point(size=2)
```

Answer: package name: ggplot2 (1 mark), scatter plot (2 marks).

(c) Based on the boxplot below, 

```{r}
library(ggplot2)
ggplot(diamonds[1:10000,], aes(x=cut, y=price, fill=cut)) + geom_boxplot()
```

Compare the medians of price among different cut, give comments on the boxplot, large difference  in price or not based on cut? (4 marks)

Answer: The medians are barely same, there is not large difference.

#### Question 2 (15 marks)

Suppose we are modeling a simple linear regression, y is the independent variable and x is the dependent variable. 

```{r}
x<-c(1,3,4,7,8)
y<-c(12,11,7,5,3)
cbind(x,y)
```


(a) Write down the true model. (2 marks)

Answer:  $y=\beta_0+\beta_1x+\epsilon$  (2 marks)

(b) Write down the estimated model. (2 marks)

Answer:  $\hat{y}=\hat{\beta}_0+\hat{\beta}_1x$ or $\hat{y}=b_0+b_1x$  (2 marks)

(c) Write down the residual. (2 marks)

Answer:  $e=y-\hat{y}$ or ($\hat{\epsilon}=y-\hat{y}$ )  (2 marks)

(d) What is the assumption of the residual $\epsilon$ (Hint: What is the distribution)? (2 marks)

Answer: 

  1. We assume the $\epsilon$ follows normal distribution with mean 0 and a constant     standard deviation. (1 mark)
  2. The error terms are independent. (1 mark)


(e) Find the sample correlation coefficient $r$ between $x$ and $y$, by the formula. (4 marks)

$$r=\frac{\sum(x-\bar{x})(y-\bar{y})}{\sqrt{\sum(x-\bar{x})^2\sum(y-\bar{y})^2}}=\frac{\sum(x-\bar{x})(y-\bar{y})}{(n-1)s_xs_y}$$
(given $\sum(x-\bar{x})(y-\bar{y})= -42.8$, $s_x=2.88$, $s_y=3.85$)

Answer: 

```{r}
cor(x,y)
```

(f) Find the least square estimators $\hat{\beta}_0$ and $\hat{\beta}_1$, by the formula. (3 marks)

$$\hat{\beta}_1=b_1=r\frac{s_y}{s_x} , \quad \hat{\beta}_0=b_0=\bar{y}-b_1\bar{x}$$
Answer:

```{r}
summary(lm(y~x))
```
